A Survey on Ordered Binary Decision Diagrams

### 2015-09-10 paper.tex
Fix wording

Figure~\ref{subfig:obdd} shows the result of applying the first two transformation
rules to the BDD shown in Figure~\ref{subfig:bdd}. The third rule is shown
in Figure~\ref{fig:redundant-nonterminals}.
Figure~\ref{subfig:redundant-nonterminals-before} shows a BDD with redundant
nonterminal nodes (both \textbf{B}'s, in essence) and
Figure~\ref{subfig:redundant-nonterminals-after} shows the equivalent OBDD without
redundant nonterminals. \tbr

>>>>

Figure~\ref{fig:bdd-and-obdd} shows the result, \ref{subfig:obdd}, of applying
the first two transformation rules to the BDD shown in \ref{subfig:bdd}.
The third rule is shown in Figure~\ref{fig:redundant-nonterminals}.
Figure~\ref{subfig:redundant-nonterminals-before} shows a BDD with redundant
nonterminal nodes (both B's, in essence) and
Figure~\ref{subfig:redundant-nonterminals-after} shows the equivalent OBDD
without redundant nonterminals. \tbr
